### 2020-09-13 code/figure4.Rmd
Reduce y-axis text size for fig4

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,
                   color = cluster,
                   group = cluster)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_pointrange(aes(xmin = ci.low, xmax = ci.up, fatten = 1)) +
  scale_y_discrete(labels = Hugo_rownames) +
  scale_color_manual(values = cluster_colors) +
  theme_classic() +
  xlab("log odds ratio") +
  ylab("Gene") +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y", switch = "y") +
  theme(
    panel.grid.major.y = element_line(colour = "#f0f0f0"),
    axis.text.y = element_text(size = 8),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8)
  )

>>>>

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,
                   color = cluster,
                   group = cluster)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_pointrange(aes(xmin = ci.low, xmax = ci.up, fatten = 1)) +
  scale_y_discrete(labels = Hugo_rownames) +
  scale_color_manual(values = cluster_colors) +
  theme_classic() +
  xlab("log odds ratio") +
  ylab("Gene") +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y", switch = "y") +
  theme(
    panel.grid.major.y = element_line(colour = "#f0f0f0"),
    axis.text.y = element_text(size = 6.5),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8)
  )
